Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-08-23 analysis/report/effectiveness_report_comparetimescales.Rmd
better plots

  plot_effects <-
    ggplot(data = tidy_effects) +
    geom_point(aes(y=exp(estimate), x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_linerange(aes(ymin=exp(conf.low), ymax=exp(conf.high), x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_hline(aes(yintercept=1), colour='grey')+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(breaks=unique(tidy_effects$term_left), limits=c(min(tidy_effects$term_left), max(tidy_effects$term_right)+1), expand = c(0, 0))+
    scale_y_log10(
    breaks=c(0.1, 0.125, 0.25, 0.33, 0.5, 0.75, 1, 1.33, 2, 3, 4, 8,10),
    sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
  )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=2))+
    labs(
      y="Hazard ratio",#\nChAdOx1 / BNT162b2",
      x="Days since vaccination",
      colour=NULL
     ) +
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  plot_spline <-
    ggplot(spline)+
    geom_hline(aes(yintercept=1), colour='grey')+
    geom_line(aes(x=tstop-1, y=hr, colour=model_name))+
    geom_ribbon(aes(x=tstop-1, ymin=hr.ll, ymax=hr.ul, fill=model_name), alpha=0.2, colour="transparent")+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_log10(
      breaks=c(1/8, 1/6, 0.25, 0.33, 0.5, 0.67, 1, 1.5, 2, 3, 4, 6, 8),
      sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=1))+
    scale_fill_brewer(type="qual", palette="Set2", guide="none")+
    labs(
      x = "Days since first dose",
      y = "Hazard ratio",
      colour = NULL, fill=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

>>>>

  plot_effects <-
    ggplot(data = tidy_effects) +
    geom_point(aes(y=exp(estimate), x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_linerange(aes(ymin=exp(conf.low), ymax=exp(conf.high), x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_hline(aes(yintercept=1), colour='grey')+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(
      breaks = seq(0, 7*52, 14), 
      limits = c(min(tidy_effects$term_left), 14*7), 
      expand = c(0, 0)
    )+
    scale_y_log10(
    breaks=c(0.125, 0.167, 0.25, 0.333, 0.5, 0.667, 1, 1.5, 2, 3, 4, 6, 8),
    sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
  )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=2))+
    labs(
      y="Hazard ratio",#\nChAdOx1 / BNT162b2",
      x="Days since vaccination",
      colour=NULL
     ) +
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  plot_spline <-
    ggplot(spline)+
    geom_hline(aes(yintercept=1), colour='grey')+
    geom_line(aes(x=tstop-1, y=hr, colour=model_name))+
    geom_ribbon(aes(x=tstop-1, ymin=hr.ll, ymax=hr.ul, fill=model_name), alpha=0.2, colour="transparent")+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_log10(
      breaks=c(0.125, 0.167, 0.25, 0.333, 0.5, 0.667, 1, 1.5, 2, 3, 4, 6, 8),
      sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=1))+
    scale_fill_brewer(type="qual", palette="Set2", guide="none")+
    labs(
      x = "Days since first dose",
      y = "Hazard ratio",
      colour = NULL, fill=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),
